\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-04-28 paper.tex
Do not mention TBOX immutable in Prolog
Fix #12

It also has notable limitations, both fundamental (the suitability of
Description Logics when reasoning on --typically non-monotonic-- commonsense
knowledge is questionable) and practical: RDF triples imply only binary
predicates, which constrains the expressiveness of the system or leads to
cumbersome reifications. Alternatives exist (like {\sc
KnowRob}~\cite{Tenorth2009a}) that mix RDF with more expressive logic languages
like {\sc Prolog}, at the price, however, of other limitations, like
closed-world reasoning or immutable T-Box. The classification performance is
another issue: from our experience, with an ontology sized for a standard
experiment (about 100 classes and 200 instances), classification typically
takes about 100ms, which becomes problematic during interactions.  Besides, the
performances are difficult to predict, since a seemingly inoffensive new
statement may indirectly change abruptly the logical complexity of the whole
knowledge model and lead to notable degradation of classification time.

>>>>

It also has notable limitations, both fundamental (the suitability of
Description Logics when reasoning on --typically non-monotonic-- commonsense
knowledge is questionable) and practical: RDF triples imply only binary
predicates, which constrains the expressiveness of the system or leads to
cumbersome reifications. Alternatives exist (like {\sc
KnowRob}~\cite{Tenorth2009a}) that mix RDF with more expressive logic languages
like {\sc Prolog} with other limitations, like closed-world reasoning. The
classification performance is another issue: from our experience, with an
ontology sized for a standard experiment (about 100 classes and 200 instances),
classification typically takes about 100ms, which becomes problematic during
interactions.  Besides, the performances are difficult to predict, since a
seemingly inoffensive new statement may indirectly change abruptly the logical
complexity of the whole knowledge model and lead to notable degradation of
classification time.
